---
title: "Study2_analysis_working"
output: html_document
date: "2024-09-18"
---

```{r setup, include=FALSE}

#install.packages(c("lavaan", "mirt", "MplusAutomation", "psych", "polycor", "thurstonianIRT"))
library(lavaan)
library(mirt)
library(MplusAutomation)
library(psych)
library(polycor)
library(readr)
library(dplyr)
library(janitor)
library(semPlot)
library(thurstonianIRT)
library(tidyverse)

```


```{r load data, echo=FALSE}

data <- read_csv("Study2_200.csv")

```
# CFA Model 2: SS Maladaptive Personality (G-60-SS)

```{r ss2 data, echo=FALSE}

SS2_items <- data[, 1:60]
SS2_items <- sapply(SS2_items, as.numeric)

SS2_items <- SS2_items %>% 
  remove_empty(which=c("rows","cols"))


#summary(SS2_items)

```

```{r ss2 data, echo=FALSE}

SS1_items <- data %>% 
  select(I1:B35)

SS1_items <- sapply(SS1_items, as.numeric)

SS1_items <- SS1_items %>% 
  remove_empty(which=c("rows","cols"))


#summary(SS1_items)

```


This CFA model is specified and fitted to data based on G-60-SS in Geunole et al's (2016) paper 

```{r model, echo=FALSE}

model_SS2 <- '
  CO =~ G1+G4+G7+G17+G25+G35+G37+G44+G49+G56
  DE =~ G2+G11+G19+G23+G26+G31+G38+G46+G57+G59
  NE =~ G3+G5+G21+G24+G30+G32+G41+G45+G51+G53
  PS =~ G6+G9+G15+G18+G27+G33+G42+G48+G54+G60 
  AN =~ G10+G13+G16+G22+G28+G34+G40+G43+G52+G55
  DI =~ G8+G12+G14+G20+G29+G36+G39+G47+G50+G58
'

cat(model_SS2)

```
Geonole's paper: 

The model was fitted to the polychoric correlations of ordered categorical item responses.
employing the diagonally weighted least squares (DWLS) estimator with robust errors for all
estimations.
For the DWLS and ULS estimators, lavaan provides ‘robust’ variants: WLSM, WLSMVS, WLSMV, ULSM, ULSMVS, ULSMV.

```{r fit model, echo=FALSE}

fit_ss2 <- cfa(model_SS2, data= SS2_items,
               estimator = "WLSMVS") 

lavInspect(fit_ss2, "cov.lv")

#summary(fit_ss2, fit.measures = TRUE, standardized = TRUE)

```

```{r plot model, echo=FALSE}

ss2_graph <- semPaths(object = fit_ss2, nCharNodes = 0)

ss2_plot <- semPaths(object = fit_ss2,
         whatLabels = "std",          # Show standardised estimates on the figure
         nCharNodes = 0,
         style = "lisrel",
         covAtResiduals = FALSE,
         exoVar = FALSE,
         layoutSplit = FALSE,
         layout = "tree",
         rotation = 2,
         edge.color = "black",
         color = "pink",
        sizeLat = 7,
         sizeLat2 = 4,
         sizeMan = 3,
         sizeMan2 = 2,
         border.width = 0.5,
         edge.label.cex = 0.35,
         edge.width = 0.3
         )  
```

```{r fit measure}

# Extract fit measures
fitmeasures(fit_ss2, c("chisq", "df", "pvalue", "cfi", "srmr", "rmsea"))

# Extract SS2 CFA model factor correlations
ss2_cor <- lavInspect(fit_ss2, "cor.lv")

print(ss2_cor)

```

# CFA Model 1: SS influence tactics based on K&M and Buss resuls 

24 manipulation tactics from (Buss et al., 1987), factor structure based on Buss's factor loading results (orginially for intimate relationship context) items were neutralized in ways suggested in Ketterman & Maner, 2021/ similar to how Jonason & Webster_2012 did it 

27 additional tactics items developed from Ketterman & Maner, 2021, factor structure was adapted from their EFA factor loading results. 

From Ketterman & Maner, 2021: 27
AU= Authority (12)
RB =Relationship Building (9)
EX = Explanation

24 manipulation tactics from (Buss et al., 1987):

CH = Charm (5)
ST = Silent Treatment (4)
CO = Coercion (5)
RS = Reason (5)
RG = Regression (2)
DB = Debasement (3)


```{r model, echo=FALSE}

model_SS1 <- '
  AU =~ I1 + I2 + I3 + I5 + I6 + I7 + I8 + I9 + I10 + I22 + I31 + I33
  RB =~ I13 + I14 + I24 + I25 + I26 + I27 + I28 + I29 + I30
  EX =~ I15 + I16 + I17 + I18 + I19+ I21
  CH =~ B4 + B9 + B19 + B24 + B29
  ST =~ B22 + B12 + B17 + B32
  CO =~ B3 + B23 + B13 + B33 +B28
  RS =~ B11 + B31 + B34 + B6
  RG =~ B2 + B7 
  DB =~ B35 + B30 + B15
'

cat(model_SS1)

```

```{r fit model, echo=FALSE}

fit_ss1 <- cfa(model_SS1, data= SS1_items,
               estimator = "WLSMVS") 

lavInspect(fit_ss1, "cov.lv")

summary(fit_ss1, fit.measures = TRUE, standardized = TRUE)

```



```{r plot model, echo=FALSE}

ss1_graph <- semPaths(object = fit_ss1, nCharNodes = 0)

ss1_plot <- semPaths(object = fit_ss1,
         whatLabels = "std",          # Show standardised estimates on the figure
         nCharNodes = 0,
         style = "lisrel",
         covAtResiduals = FALSE,
         exoVar = FALSE,
         layoutSplit = FALSE,
         layout = "tree",
         rotation = 1,
         edge.color = "black",
         color = "pink",
        sizeLat = 7,
         sizeLat2 = 3,
         sizeMan = 1.2,
         sizeMan2 = 2,
         border.width = 0.5,
         edge.label.cex = 0.4,
         edge.width = 0.3
         )  
```


```{r fit measure}

# Extract fit measures
fitmeasures(fit_ss1, c("chisq", "df", "pvalue", "cfi", "srmr", "rmsea"))

# Extract SS2 CFA model factor correlations
ss1_cor <- lavInspect(fit_ss1, "cor.lv")

print(ss1_cor)

```

# CFA Model 3: SS Maladaptive Personality X Coercion and Complaisant (G-60-SS)

Based On K&M's EFA results:


model_SS1 <- '
  AU =~ I1 + I2 + I3 + I5 + I6 + I7 + I8 + I9 + I10 + I22 + I31 + I33
  RB =~ I13 + I14 + I24 + I25 + I26 + I27 + I28 + I29 + I30
  EX =~ I15 + I16 + I17 + I18 + I19+ I21
  CH =~ B4 + B9 + B19 + B24 + B29
  ST =~ B22 + B12 + B17 + B32
  CO =~ B3 + B23 + B13 + B33 +B28
  RS =~ B11 + B31 + B34 + B6
  RG =~ B2 + B7 
  DB =~ B35 + B30 + B15
  
  
Coercive tactics (CO): CH, ST, CO, RG, DB, AU
Complaisant tactics (CP): RS, EX, RB


```{r data, echo=FALSE}

# Convert SS1_items to a data frame
SS1_items <- as.data.frame(SS1_items)

# Now you can use mutate()
SS3_items <- SS1_items %>% 
  mutate(AU = (I1+I2+I3+I5+I6+I7+I8+I9+I10+I22+I31+I33)/12) %>%
  mutate (RB = (I13 + I14 + I24 + I25 + I26 + I27 + I28 + I29 + I30)/9) %>%
  mutate(EX = (I15 + I16 + I17 + I18 + I19+ I21)/6)%>%
  mutate(CH = (B4 + B9 + B19 + B24 + B29)/5) %>%
  mutate (ST = (B22 + B12 + B17 + B32)/4) %>%
  mutate (CO = (B3 + B23 + B13 + B33 +B28)/5) %>%
  mutate (RS = (B11 + B31 + B34 + B6)/4) %>%
  mutate (RG = (B2 + B7)/2) %>%
  mutate (DB = (B35 + B30 + B15)/3)
  

```

```{r model, echo=FALSE}
#Coercive tactics (Coer): CH, ST, CO, RG, DB, AU
#Complaisant tactics (Comp): RS, EX, RB

model_SS3 <- '
  Coer =~ CH + ST + CO + RG + DB+ AU
  Comp =~ RS + EX + RB
'

cat(model_SS3)

```

```{r fit model, echo=FALSE}

fit_ss3 <- cfa(model_SS3, data= SS3_items,
               estimator = "WLSMVS")  #not sure if this is now continuous variables, if yes, changed to MLE

lavInspect(fit_ss3, "cov.lv")

summary(fit_ss3, fit.measures = TRUE, standardized = TRUE)

```



```{r plot model, echo=FALSE}

ss1_graph <- semPaths(object = fit_ss3, nCharNodes = 0)

ss1_plot <- semPaths(object = fit_ss3,
         whatLabels = "std",          # Show standardised estimates on the figure
         nCharNodes = 0,
         style = "lisrel",
         covAtResiduals = FALSE,
         exoVar = FALSE,
         layoutSplit = FALSE,
         layout = "tree",
         rotation = 1,
         edge.color = "black",
         color = "pink",
        sizeLat = 7,
         sizeLat2 = 4,
         sizeMan = 5,
         sizeMan2 = 2,
         border.width = 0.5,
         edge.label.cex = 0.5,
         edge.width = 1
         )  
```


```{r fit measure}

# Extract fit measures
fitmeasures(fit_ss3, c("chisq", "df", "pvalue", "cfi", "srmr", "rmsea"))

# Extract SS2 CFA model factor correlations
ss3_cor <- lavInspect(fit_ss3, "cor.lv")

print(ss3_cor)

```

```{r block structure}

lambdas <- c(runif(6, 0.5, 1), runif(6, -1, -0.5))

sim_data <- sim_TIRT_data(
npersons = 100,
ntraits = 3,
nblocks_per_trait = 4,
gamma = 0,
lambda = lambdas,
Phi = diag(3)
)
cat(make_lavaan_code(sim_data)) 

#Generate lavaan code for Thurstonian IRT models

```

#FC Model 2: G-60-FC

trait 1= CO = Compulsiveness; 
trait 2= DE = Detachment; 
trait 3= NE = Negative Affect; 
trait 4= PS = Psychoticism; 
trait 5= DI = Disinhibition; 
trait 6= AN = Antagonism.

  fixed correalations
  
  AN ~~ 0.649*DI (6/5)
  AN ~~ 0.236*NE (6/3)
  DI ~~ 0.635*NE (5/3)
```{r block structure}

#Pull FC data for G-60-FC
fc2_data <- data %>%
  select(GF1:GF60)

write.csv(fc2_data, file = "fc2_data.csv")

fc2_blocks <- 
  set_block(items=c("GF1", "GF2", "GF3"), traits = c("CO", "DE", "NE")) +
  set_block(items=c("GF4", "GF5", "GF6"), traits = c("CO", "NE", "PS")) +
  set_block(items=c("GF7", "GF8", "GF9"), traits = c("CO", "DI", "PS")) +
  set_block(items=c("GF10", "GF11", "GF12"), traits = c("AN", "DE", "DI")) +
  set_block(items=c("GF13", "GF14", "GF15"), traits = c("AN", "DI", "PS")) +
  set_block(items=c("GF16", "GF17", "GF18"), traits = c("AN", "CO", "PS")) +
  set_block(items=c("GF19", "GF20", "GF21"), traits = c("DE", "DI", "NE")) +
  set_block(items=c("GF22", "GF23", "GF24"), traits = c("AN", "DE", "NE")) +
  set_block(items=c("GF25", "GF26", "GF27"), traits = c("CO", "DE", "PS")) +
  set_block(items=c("GF28", "GF29", "GF30"), traits = c("AN", "DI", "NE")) +
  set_block(items=c("GF31", "GF32", "GF33"), traits = c("DE", "NE", "PS")) +
  set_block(items=c("GF34", "GF35", "GF36"), traits = c("AN", "CO", "DI")) +
  set_block(items=c("GF37", "GF38", "GF39"), traits = c("CO", "DE", "DI")) +
  set_block(items=c("GF40", "GF41", "GF42"), traits = c("AN", "NE", "PS")) +
  set_block(items=c("GF43", "GF44", "GF45"), traits = c("AN", "CO", "NE")) +
  set_block(items=c("GF46", "GF47", "GF48"), traits = c("DE", "DI", "PS")) +
  set_block(items=c("GF49", "GF50", "GF51"), traits = c("CO", "DI", "NE")) +
  set_block(items=c("GF52", "GF53", "GF54"), traits = c("AN", "NE", "PS")) +
  set_block(items=c("GF55", "GF56", "GF57"), traits = c("AN", "CO", "DE")) +
  set_block(items=c("GF58", "GF59", "GF60"), traits = c("DI", "DE", "PS"))

```

```{r triplet}

# generate the data to be understood by 'thurstonianIRT'

fc2_triplets <- make_TIRT_data(
  data = fc2_data, 
  blocks = fc2_blocks, 
  direction = "larger",
  format = c("ranks", "pairwise"), 
  family = "bernoulli", 
  range = c(0, 1))

#cat(make_lavaan_code(fc2_triplets)) 


```

Choice of estimator 

using the DWLS estimator with mean corrected Satorra–Bentler goodness-of-fit tests. Note that this estimation procedure is denoted as WLSM estimation in Mplus.
(Brown & Maydeu-Olivares, 2011)
The mean and variance adjustment for the ULS estimation is denoted as “estimator” ULSMV in Mplus, and it is denoted WLSMV for the DWLS estimation. (Brown & Maydeu-Olivares, 2012)

ULSMV/ Mplus used in Watrin et al 2019 

DWLS; lavaan also provides ‘robust’ variants for DWLS : WLSM, WLSMVS, WLSMV, ULSM, ULSMVS, ULSMV 
no clear indication of which one of these was used in Geonole, 2016


In originial model (Geonole, 2016), initial identification also failed. 
They constrained correlation between AN (Antagonism), DI (Disinhibition), and NE (Negative Affect).

       CO     DE     NE     PS     AN     DI
CO  1.000                                   
DE -0.683  1.000                            
NE -0.844  0.751  1.000                     
PS -0.621  0.683  0.667  1.000              
AN -0.193  0.465  0.236  0.663  1.000       
DI -0.891  0.617  0.635  0.748  0.649  1.000


```{r fit data}

# fit the data using lavaan

fc2_fit <- fit_TIRT_lavaan(fc2_triplets, estimator = "WLSMV")

```

```{r summary fit}
# View results
print(fc2_fit)
predict(fc2_fit)


# store results 
fc2_traits_TIRT <- predict(fc2_fit)

```

```{r  fit}
# View results
summary(fc2_fit, fit.measures = TRUE)
fc2_summary

 gof(fc2_fit) # Extract corrected goodness of fit statistics for gof.TIRTfit 

```

```{r fc1 results}

#create results list

FC2_results <- list()

fc2_traits_TIRT_s <- fc2_traits_TIRT %>% pivot_wider(id_cols = id, names_from = trait,
                                                 values_from = c(estimate))

FC2_results$final_estimates <- fc2_traits_TIRT_s #Final trait score and standard error estimates 

FC2_results$fit_object <- fc2_fit #TIRT model fit object

FC2_results$responses_TIRT <- fc2_triplets #The long format TIRT response 

FC2_results$long_estimates <- fc2_traits_TIRT #Final trait score and standard error estimates, in long format 

FC2_results

```

```{r fc2 correlation}

#Extract correlation matrix from final estimates 
fc2_correlation_matrix <- cor(FC2_results$final_estimates)
print(fc2_correlation_matrix)

```

              id      trait1     trait2      trait3       trait4       trait5      trait6
id      1.00000000 -0.09920042  0.0174109 -0.03964689  0.058018276 -0.100306553 -0.05994578
trait1 -0.09920042  1.00000000 -0.2500330  0.50442840  0.504520897  0.552058955  0.55830720
trait2  0.01741090 -0.25003299  1.0000000 -0.43831446 -0.195025642 -0.280347802 -0.38663224
trait3 -0.03964689  0.50442840 -0.4383145  1.00000000  0.398582212  0.755552729  0.72452263
trait4  0.05801828  0.50452090 -0.1950256  0.39858221  1.000000000  0.008533176  0.15671114
trait5 -0.10030655  0.55205895 -0.2803478  0.75555273  0.008533176  1.000000000  0.73364411
trait6 -0.05994578  0.55830720 -0.3866322  0.72452263  0.156711139  0.733644113  1.00000000


#FC Model 1: FC influence tactics 

```{r data}
#Pull FC data for G-60-FC
fc1_data <- data %>%
  select(S1T1_1:S4T5_3)
```
  
  
trait 1= LH 
trait 2 = MH 
trait 3 = ML
trait 4 = LM
trait 5 = MM
trait 6 = HL

```{r block structure}

fc1_blocks <- 
  set_block(c("S1T1_1", "S1T1_2", "S1T1_3"), traits = c("L_H", "M_H", "M_L")) +
  set_block(c("S1T2_1", "S1T2_2", "S1T2_3"), traits = c("L_M", "M_H", "M_M")) +
  set_block(c("S1T3_1", "S1T3_2", "S1T3_3"), traits = c("H_L", "M_L", "M_M")) +
  set_block(c("S1T4_1", "S1T4_2", "S1T4_3"), traits = c("L_H", "L_M", "M_L")) +
  set_block(c("S1T5_1", "S1T5_2", "S1T5_3"), traits = c("H_L", "L_H", "L_M")) +
  set_block(c("S2T1_1", "S2T1_2", "S2T1_3"), traits = c("L_H", "M_H", "M_L")) +
  set_block(c("S2T2_1", "S2T2_2", "S2T2_3"), traits = c("L_M", "M_H", "M_M")) +
  set_block(c("S2T3_1", "S2T3_2", "S2T3_3"), traits = c("H_L", "M_L", "M_M")) +
  set_block(c("S2T4_1", "S2T4_2", "S2T4_3"), traits = c("L_H", "L_M", "M_L")) +
  set_block(c("S2T5_1", "S2T5_2", "S2T5_3"), traits = c("H_L", "L_H", "L_M")) +
  set_block(c("S3T1_1", "S3T1_2", "S3T1_3"), traits = c("L_H", "M_H", "M_L")) +
  set_block(c("S3T2_1", "S3T2_2", "S3T2_3"), traits = c("L_M", "M_H", "M_M")) +
  set_block(c("S3T3_1", "S3T3_2", "S3T3_3"), traits = c("H_L", "M_L", "M_M")) +
  set_block(c("S3T4_1", "S3T4_2", "S3T4_3"), traits = c("L_H", "L_M", "M_L")) +
  set_block(c("S3T5_1", "S3T5_2", "S3T5_3"), traits = c("H_L", "L_H", "L_M")) +
  set_block(c("S4T1_1", "S4T1_2", "S4T1_3"), traits = c("L_H", "M_H", "M_L")) +
  set_block(c("S4T2_1", "S4T2_2", "S4T2_3"), traits = c("L_M", "M_H", "M_M")) +
  set_block(c("S4T3_1", "S4T3_2", "S4T3_3"), traits = c("H_L", "M_L", "M_M")) +
  set_block(c("S4T4_1", "S4T4_2", "S4T4_3"), traits = c("L_H", "L_M", "M_L")) +
  set_block(c("S4T5_1", "S4T5_2", "S4T5_3"), traits = c("H_L", "L_H", "L_M"))

```

```{r triplet}

# generate the data to be understood by 'thurstonianIRT'

fc1_triplets <- make_TIRT_data(
  data = fc1_data, 
  blocks = fc1_blocks, 
  direction = "larger",
  format = c("ranks", "pairwise"), 
  family = "bernoulli", 
  range = c(0, 1))

cat(make_lavaan_code(fc1_triplets)) 


```


ULSMV used in Watrin et al 2019 

WLSMVS in Brown 2011

DWLS; lavaan also provides ‘robust’ variants for DWLS : WLSM, WLSMVS, WLSMV, ULSM, ULSMVS, ULSMV 
no clear indication of which one of these was used in Geonole, 2016
```{r fit data}
# fit the data using lavaan

fc1_fit <- fit_TIRT_lavaan(fc1_triplets, estimator = "WLSMV") #or WLSMVS
```

```{r summary fit}
# View results
print(fc1_fit)

# store results 
fc1_traits_TIRT <- predict(fc1_fit)

```

```{r  fit}
# View results
gof(fc1_fit) 


```

```{r fc1 results}

#create results list

FC1_results <- list()

fc1_traits_TIRT_s <- fc1_traits_TIRT %>% pivot_wider(id_cols = id, names_from = trait,
                                                 values_from = c(estimate))

FC1_results$final_estimates <- fc1_traits_TIRT_s #Final trait score and standard error estimates 

FC1_results$fit_object <- fc1_fit #TIRT model fit object

FC1_results$responses_TIRT <- fc1_triplets #The long format TIRT response 

FC1_results$long_estimates <- fc1_traits_TIRT #Final trait score and standard error estimates, in long format 

FC1_results


```

trait 1= LH 
trait 2 = MH 
trait 3 = ML
trait 4 = LM
trait 5 = MM
trait 6 = HL


               id     trait1     trait2     trait3     trait4     trait5     trait6
id      1.0000000 -0.1690044 -0.1731204 -0.1657489  0.1719163 -0.1610449  0.1781874
trait1 -0.1690044  1.0000000  0.9475108  0.9381057 -0.9568743  0.9712433 -0.9227964
trait2 -0.1731204  0.9475108  1.0000000  0.8730034 -0.9128604  0.9586456 -0.9010808
trait3 -0.1657489  0.9381057  0.8730034  1.0000000 -0.9625228  0.8773428 -0.9825311
trait4  0.1719163 -0.9568743 -0.9128604 -0.9625228  1.0000000 -0.9509606  0.9719931
trait5 -0.1610449  0.9712433  0.9586456  0.8773428 -0.9509606  1.0000000 -0.8830561
trait6  0.1781874 -0.9227964 -0.9010808 -0.9825311  0.9719931 -0.8830561  1.0000000


```{r fc1 correlation}

#Extract correlation matrix from final estimates 
fc1_correlation_matrix <- cor(FC1_results$final_estimates)
print(fc1_correlation_matrix)

```

```{r fc1 plot}

#plot
fc1_graph <- plot(FC1_results$final_estimates)


```


#Validation: MTMM 

##Correlation matrix of SS3xFC1 (2x6)

```{r factor scores SS3/FC1}

# 1. Extract Factor Scores (as before)
factor_scores_ss3 <- lavPredict(fit_ss3) # CFA (2 traits) estiamte factor scores 
factor_scores_fc1 <- fc1_traits_TIRT_s %>%
  select (-id)# TIRT (6 traits) estimate factor scores 

# 2. Combine Scores into a Data Frame
combined_scores1 <- data.frame(
  Coercive = factor_scores_ss3[, 1],
  Complaisant = factor_scores_ss3[, 2],
  L_H = factor_scores_fc1[, 1],
  M_H = factor_scores_fc1[, 2],
  M_L = factor_scores_fc1[, 3],
  L_M = factor_scores_fc1[, 4],
  M_M = factor_scores_fc1[, 5],
  H_L = factor_scores_fc1[, 6]
)

```

```{r matrix SS3/FC1}

# 3. Calculate Correlation Matrix (2x6)
correlation_matrix_2x6 <- cor(combined_scores1[, 1:2], combined_scores1[, 3:8]) 

colnames(correlation_matrix_2x6) <- c("LH", "MH", "ML", "LM", "MM", "HL")


# 4. Print the Correlation Matrix
print(correlation_matrix_2x6)

mean(correlation_matrix_2x6)

```

```{r plot SS3/FC1}

plot2x6 <- corrplot(correlation_matrix_2x6, method = "color", 
                    tl.col = "black", tl.srt = 45, addCoef.col = "black")
plot2x6

```

##Correlation matrix of SS1xFC1 (9x6)

Charm = MM
Silent treatment = HL 
Coercion = HL 
Reason = LH
Regression = HL
Debasement = HL
Authority = HL 
Relationship building = LM 
Explanation = LM


```{r factor scores SS1/FC1}

# 1. Extract Factor Scores (as before)
factor_scores_ss1 <- lavPredict(fit_ss1) # estimate CFA (9 traits) factor scores 
factor_scores_fc1 <- fc1_traits_TIRT_s # estimate TIRT (6 traits) factor scores 

# 2. Combine Scores into a Data Frame
combined_scores <- data.frame(
  AU_HL = factor_scores_ss1[, 1],
  RB_LM = factor_scores_ss1[, 2],
  EX_LM = factor_scores_ss1[, 3],
  CH_MM = factor_scores_ss1[, 4],
  ST_HL = factor_scores_ss1[, 5],
  CO_HL = factor_scores_ss1[, 6],
  RS_LH = factor_scores_ss1[, 7],
  RG_HL = factor_scores_ss1[, 8],
  DB_HL = factor_scores_ss1[, 9],
  LH = factor_scores_fc1[, 2],
  MH= factor_scores_fc1[, 3],
  ML= factor_scores_fc1[, 4],
  LM = factor_scores_fc1[, 5],
  MM = factor_scores_fc1[, 6],
  HL = factor_scores_fc1[, 7] 
)

```

```{r matrix SS1/FC1}

# 3. Calculate Correlation Matrix (2x6)
correlation_matrix_9x6 <- cor(combined_scores[, 1:9], combined_scores[, 10:15]) 

colnames(correlation_matrix_9x6) <- c("LH", "MH", "ML", "LM", "MM", "HL")

# 4. Print the Correlation Matrix
print(correlation_matrix_9x6)

# 5. Mean Correlation 

mean(correlation_matrix_9x6)


```

```{r plot SS1/FC1}

plot2x6 <- corrplot(correlation_matrix_9x6, method = "color", 
                    tl.col = "black", tl.srt = 45, addCoef.col = "black")
plot2x6

```